Call Center Regression Data Analysis

### 2022-11-14 References/Manuscript.tex
commit #update

\begin{abstract}
 With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
 in the United States alone, call centers play a pivotal role in a business' success.In this paper, call center volume was forecasted and
 models were created to predict the number of agents needed to meet critical attributes such as waittime, calltime, and holdtime. 
 Forecasting gives businesses the ability to make informed business decision and develop data-driven strategies. In the literature it is very
 common to see call center volume being predicted using different techniques, but there is very limited studies on attempting to correlate
 the number of agents needed. Through Regression techniques, there are 8 models proposed to model the number of agents needed based on waittime,
 calltime, goaltime, and the amount of calls handled.
\end{abstract}

@@

  \begin{table}[H]
    \resizebox{\textwidth}{!} {
    \begin{tabular}{ l | l |}
      {\bf Dependent Variable} & {\bf R-squared Value}\\
    \hline
    Wait Time& 0.1642 \\
    \hline
    Call Time& 0.0569\\
    \hline
    Goal Met& 0.2458\\
    \hline
    Interaction Value& 0.234\\
    \end{tabular}
    }
    \end{table}
R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
Overall, the higher the R-squared the better.
\section*{Discussion}
Overall, the best agent model would be the model with the highest R-squared value and Pearson Coefficient. In this case, this would be
AvgGoalMet= 0.986 - 0.216*CallsPerAgent. A close second place would be AvgWaittime= -5.292 + 61.148*CallsPerAgent, as it had a decent 
Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
r-squared value. Overall the other 3 models are would suggest to an individual to use to determine how many agents
there business to have. Unfortunately, there are so many aspects to just this. In regards to a business perspective, the call center must have
a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance in between to ultimately maximize efficiency.
We were also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
a week.

>>>>

\begin{abstract}
 With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
 in the United States alone, call centers play a pivotal role in a business' success.In this paper, call center volume was forecasted and
 models were created to predict the number of agents needed to meet critical attributes such as waittime, calltime, and holdtime. 
 Forecasting gives businesses the ability to make informed business decision and develop data-driven strategies. In the literature it is very
 common to see call center volume being predicted using different techniques, but there is very limited studies on attempting to correlate
 the number of agents needed. Through Regression techniques, there are 4 models proposed to model the number of agents needed based on waittime,
 calltime, goaltime, and the amount of calls handled.
\end{abstract}

@@

  \begin{table}[H]
    \resizebox{\textwidth}{!} {
    \begin{tabular}{ l | l |}
      {\bf Dependent Variable} & {\bf R-squared Value}\\
    \hline
    Wait Time& 0.1642 \\
    \hline
    Call Time& 0.0569\\
    \hline
    Goal Met& 0.2458\\
    \hline
    Interaction Value& 0.234\\
    \end{tabular}
    }
    \end{table}
R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
Overall, the higher the R-squared the better. The model with Goal Met as the dependent variable has the highest R-square value of 0.2458, followed by
the model with Interaction value with an R-squared value of 0.234, then Wait time with a R-squared value of 0.1642, and lastly Call time with a R-squared value of 0.0569.
\section*{Discussion}
Overall, the best agent model would be the model with the highest R-squared value and Pearson Coefficient. In this case, this would be
AvgGoalMet= 0.986 - 0.216*CallsPerAgent. A close second place would be AvgWaittime= -5.292 + 61.148*CallsPerAgent, as it had a decent 
Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
r-squared value. Overall the other 3 models are would suggest to an individual to use to determine how many agents
there business to have. Unfortunately, there are so many aspects to just this. In regards to a business perspective, the call center must have
a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance in between to ultimately maximize efficiency.
We were also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
a week.
